\documentclass[10pt]{article}
%\input{assignment-macros-0}
\usepackage{amssymb} %empty set character
\usepackage[paper=letterpaper,headsep=15pt,left=35pt,top=30pt,right=35pt,bottom=30pt,includeheadfoot]{geometry}
%\usepackage{times} %set font to times
\usepackage{parskip} %don't indent new paragraphs
\usepackage{enumitem} %bullet lists
\usepackage[colorlinks=true]{hyperref} %for \url
\usepackage{xstring} %pull out substrings in newcommands
%\usepackage{pifont} %dings
\usepackage{fancyhdr} %for fancy headers/footers
% \usepackage[T1]{fontenc} % Tried a new font codec but don't like
\usepackage{tipa} % for textpipe

%\setlist{nolistsep} %prevent ugly spacing in lists
\setlength{\headheight}{50pt}
%\setlength{\voffset}{0pt}
\pagestyle{fancy}
\fancyhf{} %set header line to nothing so we don't get one
\renewcommand{\headrulewidth}{0pt}

%Define commands to make bullet lists
\newlist{things}{itemize}{1}
\setlist[things]{label*=\textbullet,noitemsep,topsep=-8pt,itemsep=0pt,partopsep=0pt,after=\vspace{5pt}}
\setlist[things,1]{ref=\arabic*}
\setlist[things,2]{ref=\arabic{stepsi}.\arabic*}
\newcommand{\THINGS}{things}
\newcommand{\thing}[1][]{\item #1}

\newcommand{\sectionheader}[1]{
    \vspace{3pt}
    \StrSplit{#1}{3}{\firstpart}{\lastpart} %split string around 3rd char
    %\textbf{\LARGE\textcolor{lightgreen}{\ding{228}}} %Add an arrow
    %\textbf{\LARGE #1}\\[5pt] %just throw raw text

    \makebox[0pt][l]{\textbf{\LARGE\firstpart\lastpart}}%%
    \rule[-1ex]{\columnwidth}{.1pt}

    % \textbf{\LARGE
    %     \firstpart
    %     \lastpart
    % }\\[1pt]
    % \kern100pt
    % \hrule height .1pt
    % \kern1pt
    % \noindent\rule[0ex]{\textwidth}{.1pt}
}

\newcommand{\dates}[2]{
    \textbf{#1-#2}
    %\textbf{\textcolor{lightgreen}{#1}}
}
%\newcommand{\dates}[1]{#1}

\chead{
    \textbf{\huge Stanley \hspace{-3pt}Ari \hspace{-1pt}Cohen}\\
    5840 McCrimmon Pkwy Apt 105, Morrisville, NC 27560\\
    (760)846-6814 \textpipe{} a12n@mac.com
}

\begin{document}

    \sectionheader{Objective}
    Seeking a full time software engineering position to gain 
    experience and utilize my knowledge of physics, CS, 
    and calculus based maths.
    
    \sectionheader{Experience}
    \textbf{\large Tyler Technologies} \hfill \dates{Sept 2018}{Current}\\
    \textit{\textbf{Senior Software Engineer}}
    \begin{things}
        \thing Facilitate team scrum and retrospective meetings, promoting open communication
                    and a collaborative environment that fosters trust, engagement, and high performance.
        \thing Collaborate across multiple internal teams to coordinate and integrate efforts
                    on large-scale projects. Ensure seamless communication, alignment of goals,
                    and on-time delivery of key milestones.
        \thing Trained support representatives in SQL to perform routine data fixes independently,
                    reducing reliance on developers and saving ~800 hours of engineering time anually.
        \thing Partner with the support team to investigate and resolve client-reported software
                    issues, ensuring timely solutions and maintaining a positive customer experience.
    \end{things}

    \textbf{\large Thales USA} \hfill \dates{July 2017}{Aug 2018}\\
    \textit{\textbf{Software Engineer}}
    \begin{things}
        \thing Troubleshooted and identified systems issues in 
                    the lab prior to them being fielded.
        \thing Helped train and develop the Customer IVV and 
                    GIIV teams to ensure a better understanding of our system.
        \thing Created automation scripts to help Customer IVV
                with stress testing and bug finding.
    \end{things}

    \textbf{\large Northrop Grumman} \hfill \dates{June}{Sept 2015}\\
    \textit{\textbf{Software Design and Programming Intern}}
    \begin{things}
        \thing Used Blender to model and render pieces of the scene
                for use in simulations.
        \thing Worked in C++ and Visual Studio to develop a simulation
                plugin that utilized IEEE DIS.
        \thing Performed software regression testing to ensure requirements
                were met.
    \end{things}

    \textbf{\large La Costa Kids} \hfill \dates{June 2011}{June 2015}\\
    \textit{\textbf{Software Design Consultant}}
    \begin{things}
        \thing Designed and implemented an Objective-C solution to
                manage \textgreater30K transactions and \textgreater5K
                customers' information across 2 physical store locations.
        \thing Saved 100+ hours per year of cashier-hours looking
                up and entering transactions.
        \thing Built 3 reports and an HTML dashboard to allow for
                monitoring trends and saved 15 hours per year on tax reporting.
    \end{things}

    \textbf{\large FPAP Football Pool} \hfill \dates{June 2011}{June 2015}\\
    \textit{\textbf{Software Design Consultant}}
    \begin{things}
        \thing Designed and implmented a Python solution to manage
                manage players' betting choices and check them against
                live scores on NFL.com.
        \thing Saved the pool manager 10+ hours per week.
        \thing Delivered results to players days earlier and eliminated
                all data entry errors.
    \end{things}

    % \textbf{\large Northrop Grumman} \hfill \dates{June}{Sept 2014}\\
    % \textit{\textbf{Software Design and Programming Intern}}
    % \begin{things}
    %     \thing Worked within a team of systems engineers to develop
    %             software requirements to meet customer needs.
    %     \thing Created interactive JavaFX GUI that interfaces with a
    %             SQL database to support air vehicle management.
    % \end{things}
    % %For whatever reason there's extra space here
    % %This is down and dirty, but it works...
    % %\vspace{-13pt} 

    % \textbf{\large Scripps Research Institute} \hfill \dates{May}{Aug 2013}\\
    % \textit{\textbf{Software Design and Programming Intern}}
    % \begin{things}
    %     \thing Wrote GUI code to support medical research applications
    %     \thing Designed molecular structures for use in 3D printing
    %             to be utilized for educational outreach
    %     \thing Assembled work stations to support lab growth
    % \end{things}
    
    \sectionheader{Education}
    University California Riverside \hfill %fill line so date will right align
    \dates{Sept 2013}{June 2017}\\
    \textbf{Bachelor of Science in Computer Science}

    % Too old for this to matter now
    % \sectionheader{Projects}
    % \textbf{\large "Space Maze" Game} \hfill \dates{Jan}{Mar 2016}
    % \begin{things}
    %     \thing Constructed a game using an Arduino, Atmega1284,
    %             joystick, 16x32 LED Matrix and dual speaker system
    %     \thing A quick demo can be found at \url{https://youtu.be/efGDMYA2zpI}
    % \end{things}

    % \textbf{\large "Melody Matcher" Game} \hfill \dates{Jan}{Mar 2015}
    % \begin{things}
    %     \thing Worked in HTML, JavaScript and CSS with another
    %             CS student to build a musical educational Web App
    %     \thing The repository (with a link to the Web App) can be
    %             found at \url{https://github.com/MiaoXiao/Melody-Matcher}
    % \end{things}

    \sectionheader{Skills}
    % \vspace{-15pt} %kill the space here since we have an immediate bullet list
    \vspace{5pt} % Actually need more space now with the lines
    \begin{things}
        \thing Software Language Skills: C$^\sharp$, C/C++, Python, SQL,
                Typescript, HTML, CSS, Bash
        \thing Rational approach to problems with the ability to
                break down complex procedures into multiple tasks
                which can then easily be assigned algorithms
    \end{things}

\end{document}

